A simulation-based assessment of the relation between Stone Age sites and relative sea-level change along the Norwegian Skagerrak coast

### 2022-11-09 analysis/paper/paper.Rmd
Updated packages, checked that paper still compiles

# Create hillshade
# For some reason the terra version returned pathchy hillshade (probably due 
# to the defaults - I didn't bother experimenting too much as this is simply for
# the purposes of visualisation).
slope <- raster::terrain(raster(sitearea), 'slope')
aspect <- raster::terrain(raster(sitearea), 'aspect')
hill <- raster::hillShade(slope, aspect, 40, 270)

>>>>

# Create hillshade
# For some reason the terra version returned pathchy hillshade (probably due 
# to the defaults - I didn't bother experimenting too much as this is simply for
# the purposes of visualisation).
sraster <- raster(sitearea)
crs(sraster) <- st_crs(sitearea)$proj4string

slope <- raster::terrain(sraster, 'slope')
aspect <- raster::terrain(sraster, 'aspect')
hill <- raster::hillShade(slope, aspect, 40, 270)
